Topological Analysis of Bitcoin's Lightning Network

### 2019-01-07 article/main.tex
Privacy section is yet to come

\begin{abstract}
Bitcoin's Lightning Network (LN) is a scalability solution for Bitcoin, which allows transactions to be issued with negligible fees and settle transactions instantly at scale. In order to use LN funds need to be locked in payment channels on the Bitcoin blockchain (Layer-1), that one may use them in LN (Layer-2). LN is comprised of many payment channels forming a payment channel network. A few payment channels already enable anyone to efficiently, securely and privately route payments across the whole network. In this paper we argue that LN's current topological properties largely harms its value proposition and potential.  
\end{abstract}
\keywords{Bitcoin, Lightning Network, Network Topology, Payment Channel Network}

@@

\begin{wrapfigure}{r}{0.6\textwidth}
	\begin{center}
		\includegraphics[width=0.9\textwidth]{LNtopology.png}
	\end{center}
	\caption{LN's topology. Nodes with higher degree are highlighted with lighter colors}
	\vspace{-10pt}
\end{wrapfigure}

@@

\textbf{Our contributions.} We empirically measure and describe LN's topology and show that it is utterly centralized and fragile against both random failures and targeted attacks. These findings suggest that LN, unlike Bitcoin, is far from being reliable, censorship-resistant, decentralized and private.
\section{Lightning Network's Topology}
\begin{wrapfigure}[20]{r}{5.5cm}
	\begin{tabular}{ | l | c | }
		\hline
		Number of nodes & $2344$  \\ \hline
		Number of payment channels & $16617$  \\ \hline
		Average degree & $7.0891$ \\ \hline
		Connected components & $2$  \\ \hline
		Density & $0.00605$ \\ \hline
		Total BTC held in LN & $543.61855$\bitcoinA\\ \hline
		s-metric& $0.6878$ \\ \hline
		Maximal independent set & $1564$ \\ \hline
		Bridges & $530$ \\ \hline
		Diameter & $6$ \\ \hline
		Radius & $3$ \\ \hline
		Mean shortest path &  $2.80623$ \\ \hline
		Transitivity& $0.1046$\\ \hline
		Average clustering coefficient&$0.304$ \\ \hline
		Degree assortativity& $-0.2690$ \\ \hline
	\end{tabular}
	\caption{LN at a glance: basic properties of the LN graph.}\label{fig:properties}
\end{wrapfigure}

@@

@@

Random failures are a realistic attack vector for LN. If nodes happen to be off-line due to bad connections or other reasons, they can not participate in routing payments anymore. Such a failure can be modeled as if a node and its edges are removed from the graph. We continually remove nodes from the graph, until the networks is broken into several isolated components. The fraction of nodes need to be removed from a network to break it into multiple connected components is called critical threshold and denoted as $f_c$. As Figure~\ref{fig:randfailures} displays LN is not capable of withstanding even random failures. This incapability is even more striking when compared to other real networks.

\subsection{Targeted attacks}
Targeted attacks on LN nodes are also a major concern as the short history of LN has already shown this. On 2018 March 21st \footnote{https://www.trustnodes.com/2018/03/21/lightning-network-ddos-sends-20-nodes}, $20\%$ of nodes were down due to a Distributed Denial of Service (DDoS) attack against LN nodes. Denial of Service (DoS) attacks are also quite probable by flooding HTLCs. These attack vectors are extremely harmful, especially if they are coordinated well. One might expect that not only state-sponsored attackers will have the resources to attack a small network like LN.   
\begin{figure}[h]
	\centering
	\begin{minipage}{.5\textwidth}
		\centering
		\includegraphics[width=\linewidth]{vertexConnectivity.png}
		\captionof{figure}{LN's vertex connectivity}
		\label{fig:test1}
	\end{minipage}%
	\begin{minipage}{.5\textwidth}
		\centering
		\includegraphics[width=\linewidth]{edgeConnectivity.png}
		\captionof{figure}{LN's edge connectivity}
		\label{fig:test2}
	\end{minipage}
\end{figure}

\subsection{Fixing LN's resilience against attacks}
percolation threshold
\section{Privacy}
topological anomalies have privacy implications, low usage of tor, even tor can not help
\section{Conclusion}
false sense of security and robustness
\section{Acknowledgements}

>>>>

\begin{abstract}
Bitcoin's Lightning Network (LN) is a scalability solution for Bitcoin, which allows transactions to be issued with negligible fees and settle transactions instantly at scale. In order to use LN, funds need to be locked in payment channels on the Bitcoin blockchain (Layer-1), that one may use them in LN (Layer-2). LN is comprised of many payment channels forming a payment channel network. LN promises that a few payment channels already enable anyone to efficiently, securely and privately route payments across the whole network. In this paper we quantify the structural properties of LN and argue that LN's current topological properties largely harms its value proposition and potential.  
\end{abstract}
\keywords{Bitcoin, Lightning Network, Network Topology, Payment Channel Network}

@@

\begin{wrapfigure}{r}{0.6\textwidth}
	\captionsetup{justification=centering,margin=0.5cm}
	\begin{center}
		\includegraphics[width=0.9\textwidth]{LNtopology.png}
	\end{center}

	\caption{LN's topology. Nodes with higher degree are highlighted with lighter colors and larger circles.}\label{fig:lntopology}
	\vspace{-10pt}
\end{wrapfigure}

@@

\textbf{Our contributions.} We empirically measure and describe LN's topology and show that it is utterly centralized and fragile against both random failures and targeted attacks. These findings suggest that LN, unlike Bitcoin, is undoubtedly far from being reliable, censorship-resistant, decentralized and private.
\section{Lightning Network's Topology}
\begin{wrapfigure}[20]{r}{5.5cm}
	\begin{tabular}{ | l | c | }
		\hline
		Number of nodes & $2344$  \\ \hline
		Number of payment channels & $16617$  \\ \hline
		Average degree & $7.0891$ \\ \hline
		Connected components & $2$  \\ \hline
		Density & $0.00605$ \\ \hline
		Total BTC held in LN & $543.61855$\bitcoinA\\ \hline
		s-metric& $0.6878$ \\ \hline
		Maximal independent set & $1564$ \\ \hline
		Bridges & $530$ \\ \hline
		Diameter & $6$ \\ \hline
		Radius & $3$ \\ \hline
		Mean shortest path &  $2.80623$ \\ \hline
		Transitivity& $0.1046$\\ \hline
		Average clustering coefficient&$0.304$ \\ \hline
		Degree assortativity& $-0.2690$ \\ \hline
	\end{tabular}
	\caption{LN at a glance: basic properties of the LN graph.}\label{fig:properties}
\end{wrapfigure}

@@

When a new node joins LN, it needs to select which other nodes it is trying to connect to. In every LN implementation one of the key goal of a node is to optimize its centrality by connecting to central nodes. This phenomena sets up a preferential attachment pattern. Betweenness centrality of a node $v$ is given by the expression $g(v)=\sum_{s\neq v \neq t}\frac{\sigma_{st}(v)}{\sigma_{st}},$ where $\sigma_{st}$ is the total number of shortest paths between node $s$ and $t$, whilst $\sigma_{st}(v)$ is the number of those paths, that pass through $v$. Closeness centrality  of a node $v$ is defined as $CC(u)=\frac{N}{\sum_{u\neq v}d(u,v)},$ where $N$ is the number nodes in the graph and $d(u,v)$ is the distance between node $u$ and $v$.  Closeness centrality measures how close a node is to all other nodes.

\begin{figure}[h]
	\centering
	\begin{minipage}{.6\textwidth}
		\centering
		\includegraphics[width=\linewidth]{betweennessCentrality.png}
		\captionof{figure}{LN's betweenness centrality}
		\label{fig:betweennescentrality}
	\end{minipage}%
	\begin{minipage}{.6\textwidth}
		\centering
		\includegraphics[width=\linewidth]{closenessCentrality.png}
		\captionof{figure}{LN's closeness centrality}
		\label{fig:closenesscentrality}
	\end{minipage}
\end{figure}

Small-world architectures, like LN, exhibit high clustering with short path lenghts. The appropriate graph theoretic tool to asses clustering is the clustering coefficient \cite{watts1998collective}. Local clustering coefficient measures how well a node's neighbors are connected to each other, namely how close they are to being a clique. If a node $u$ has $deg(u)$ neighbors, then between these $deg(u)$ neighbors could be at maximum $\frac{1}{2}deg(u)(deg(u)-1)$ edges. If $N(u)$ denotes the set of $u$'s neighbors, then the local clustering coefficient is defined as $C(u)=\frac{2\mid (v,w): v,w \in N(u) \land (v,w) \in E \mid}{deg(u)(deg(u)-1)}$.

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{clusteringCoefficient.png}
	\caption{Local clustering coefficient of LN}\label{fig:localclustering}
\end{figure}

 LN's local clustering coefficient distribution suggestively captures that LN is essentially comprised of a small central clique and a loosely connected periphery.

@@

Random failures are a realistic attack vector for LN. If nodes happen to be off-line due to bad connections or other reasons, they can not participate in routing payments anymore. Such a failure can be modeled as if a node and its edges are removed from the graph. We continually remove nodes from the graph, until the networks is broken into several isolated components. The fraction of nodes need to be removed from a network to break it into multiple connected components is called critical threshold and denoted as $f_c$. As Figure~\ref{fig:randfailures}. displays LN is not capable of withstanding even random failures. This incapability is even more striking when compared to other real networks.

\subsection{Targeted attacks}
Targeted attacks on LN nodes are also a major concern as the short history of LN has already shown it. On 2018 March 21st \footnote{https://www.trustnodes.com/2018/03/21/lightning-network-ddos-sends-20-nodes}, $20\%$ of nodes were down due to a Distributed Denial of Service (DDoS) attack against LN nodes. Denial of Service (DoS) attacks are also quite probable by flooding HTLCs. These attack vectors are extremely harmful, especially if they are coordinated well. One might expect that not only state-sponsored attackers will have the resources to attack a small network like LN. In the first attack scenario we removed 30 highest-degree nodes one by one starting with the most well-connected one and gradually witdhraw the subsequent high-degree nodes. We recorded the number of connected components. As it is shown in Figure~\ref{fig:vertexconnectivity}. even just removing the highest-degree node\footnote{http://rompert.com/} fragments the LN graph into 37 connected components! Altogether the removal of the $30$ largest hubs incurs LN to collapse into $424$ components.     
\begin{figure}[h]
	\centering
	\begin{minipage}{.6\textwidth}
		\centering
		\includegraphics[width=\linewidth]{vertexConnectivity.png}
		\captionof{figure}{LN's vertex connectivity, when all the $30$ largest hubs are removed one by one}
		\label{fig:vertexconnectivity}
	\end{minipage}%
	\begin{minipage}{.6\textwidth}
		\centering
		\includegraphics[width=\linewidth]{vertexConnectivity1Removed.png}
		\captionof{figure}{LN's vertex connectivity if only one high-degree node is removed from the graph.}
		\label{fig:vertecconnectivity1removed}
	\end{minipage}
\end{figure}

We reasserted the targeted attack scenario, but for the second time we only removed one of the $30$ largest hubs and recorded the number of connected components. As it can be seen in Figure~\ref{fig:vertecconnectivity1removed} most of the hubs (25!) are so critical that their removal would be catastrophic for LN, namely they would leave behind several disconnected components.

Such network fragmentations are unwanted in case of LN, because they would make payment routing substantially more challenging (one needs to split the payment over several routes) or even impossible (there would be no routes at all). An analogous dissolution would effectively render LN non-functional.

\subsection{Fixing LN's resilience against random failures and attacks}
Designing networks which are robust to random failures and targeted attacks appear to be a conflicting desire \cite{barabasi2016network}. For instance a star graph, the simplest hub and spoke network, is resilient to random failures. The removal of any set of spokes does not hurt the connectedness of the main component. However it can not withstand a targeted attack against its central node, since it would leave behind isolated spokes.

Nonetheless, we could still enhance the network's attack tolerance by connecting its peripheral nodes \cite{barabasi2016network} and
mandating newcomers to connect to not only hubs as current implementations do but also to at least a few random nodes. This would envolve that even the removal of major hubs would leave the connectedness of the major component intact.
\section{Privacy}
topological anomalies have privacy implications, low usage of tor, even tor can not help
\section{Conclusion}
Shiny figures of LN's topology, like Figure~\ref{fig:lntopology}, convey only false sense of security and robustness.
\section{Acknowledgements}
